---
title: "new_assignment"
author: "Me"
date: "2023-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("tidyverse")
library(tidyverse)
library(stringr)
library(dplyr)
```

##Loading the datasets
```{r}

setwd("C:/UNI/Sem 3/ASSIGNMENT_1/NewAssign1/data")
Demo_DF <- read.csv("demo_train.csv")
LU_DF <- read.csv("LU_train.csv")
Token_DF <- read.csv("token_train.csv")

```
Identifying indifferences between datasets
```{r}

head(Demo_DF)
head(LU_DF)
head(Token_DF)
```
Demo_DF has a different variable for "Visit"
It seems more reasonable to keep Visit as a integer, hence a logical change would be to transform all other "Visitx." in LU_DF and Token_DF 

We have the same reverse problem for the identification of participants (Child.ID/SUBJ)
As it is written Child.ID in Demo_DF and SUBJ in the others. 
Here it seems more reasonable to change the names of the others to Child.ID since its a more specific name.
```{r}
TransformVisit = function(dataDF){
    dataDF$VISIT <- gsub("(?i)visit", "", dataDF$VISIT)
dataDF$VISIT <- as.integer(dataDF$VISIT)

    

     head(dataDF)   
}

TransformVisit(LU_DF)
TransformVisit(Token_DF)

```


